---
title: "Fayha Farooqi Linear Regression Project"
author: "Fayha Farooqi"
date: "2023-04-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(quantmod)
```

Downloading Data for Part 1
```{r}
getSymbols("CFLT", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
getSymbols("AMD", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
getSymbols("CS", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
getSymbols("ATAT", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
getSymbols("YMM", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
getSymbols("PTON", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
CFLT = c(CFLT$CFLT.Adjusted)
AMD = c(AMD$AMD.Adjusted)
CS =c(CS$CS.Adjusted)
ATAT = c(ATAT$ATAT.Adjusted)
YMM = c(YMM$YMM.Adjusted)
PTON = c(PTON$PTON.Adjusted)
df = cbind(AMD, CS, ATAT, YMM, PTON)
```
Function for part 1, first takes in a vector of adjusted prices for the stock we are trying to predict, then takes in a data frame with the adjusted close prices of the factors, as well as  a column of ones. It then outputs the coefficients of each factor, including the intercept for the ones, and returns p values of the respective classes.
```{r, warning=FALSE}
getCoefficients = function(dependentStockVector, df)
{
  df = cbind(1, df)
  xMatrix = matrix(data = df, byrow = TRUE, nrow = dim(df)[2])
  xMatrix = t(xMatrix)
  y = dependentStockVector
  Coefficients = solve(t(xMatrix) %*% xMatrix, tol = NULL) %*% t(xMatrix) %*% y
  residuals = y - xMatrix %*% Coefficients
  RSS = t(residuals) %*% residuals
  df_residuals = nrow(df) - ncol(xMatrix)
  residualStandardError = sqrt(RSS/df_residuals)
  tstat = Coefficients/(residualStandardError * sqrt(diag(solve(t(xMatrix) %*% xMatrix))))
  pValues = 2 * pt(-abs(tstat), df_residuals)
  output = cbind(Coefficients, pValues)
  colNames = colnames(df)
  colNames[1] = "Intercept"
  rownames(output) = colNames
  colnames(output) = c("Coefficients", "pValues")
  return(output)
}
```

Testing the function for part 1, using the data downloaded earlier
```{r, warning=FALSE}
getCoefficients(CFLT, df)
```
Using the built in lm function to double check my function
```{r}
testdf = cbind(CFLT, AMD, CS, ATAT, YMM, PTON)
model = lm(CFLT~ AMD + CS + ATAT + YMM + PTON, data = testdf)
summary(model)
```
Choices for step 2:
Forward Subset Selection
Adjusted Rsquared
Because I am using a forward subset selection, I will start with the most statistically significant factor, then moving down by significance.

step3:

This function outputs the RSS when given the y vector and model vector
```{r}
getRSS = function(y, model){
  output = sum((y - model)^2)
  return(output)
}
```

This function outputs the TSS when given the y vector
```{r}
getTSS = function(y){
  ybar = mean(y)
  output = sum((y - ybar)^2)
  return(output)
}
```

This function outputs the AdjRsq when given the y vector, model vector, and d value
```{r}
getAdjRsq = function(y, model, d){
  n = length(y)
  numerator = getRSS(y, model)/(n - d - 1)
  denominator = getTSS(y)/(n-1)
  return(numerator/denominator)
}
```

This function returns the Rsq value when given the y vector and model vector
```{r}
getRsq = function(y, model){
  return(1 - (getRSS(y, model)/getTSS(y)))
}
```

```{r}
getMSE = function(y, prediction){
  return(mean((y - prediction)^2))
}
```

```{r}
testdf = cbind(CFLT, AMD, CS, ATAT, YMM, PTON)
model = lm(CFLT~ AMD + CS + ATAT + YMM + PTON, data = testdf)
summary(model)
subsets = regsubsets(CFLT ~ AMD + CS + ATAT + YMM + PTON, data = testdf, method = "forward")
summary(subsets)
```

This function takes in an input that is the dependent factor, and a data frame of the independent factors and it returns the order in which the factors should be added for models with each number of factors from 1 to k
```{r}
forward_subset_selection <- function(dependent_factor, independent_factors) {
  num_factors <- ncol(independent_factors)
  current_factors <- vector(mode = "numeric", length = 0)
  best_factors <- NULL
  min_rss <- Inf
  
  for (i in seq_len(num_factors)) {
    remaining_factors <- setdiff(seq_len(num_factors), current_factors)
    model_rss <- numeric(length = length(remaining_factors))
    
    for (j in seq_along(remaining_factors)) {
      test_factors <- c(current_factors, remaining_factors[j])
      model_rss[j] <- sum(resid(lm(dependent_factor ~ ., data = independent_factors[, test_factors]))^2)
    }
    
    best_index <- which.min(model_rss)
    if (model_rss[best_index] < min_rss) {
      min_rss <- model_rss[best_index]
      best_factors <- c(current_factors, remaining_factors[best_index])
      current_factors <- best_factors
    } else {
      break
    }
  }
  
  return(list(best_factors = best_factors))
}
```

```{r, warning=FALSE}
setA = CFLT[1:46]
setB = AMD[1:46]
setC = CS[1:46]
setD = ATAT[1:46]
setE = YMM[1:46]
setF = PTON[1:46]
df = cbind(setB, setC, setD, setE, setF)

model1 = getCoefficients(setA, setF)[1] + getCoefficients(setA, setF)[2]*setF

model2 = getCoefficients(setA, cbind(setD, setF))[1] + getCoefficients(setA, cbind(setD, setF))[2]*setD + getCoefficients(setA, cbind(setD, setF))[3]*setF

model3 = (getCoefficients(setA, cbind(setD, setE, setF))[1] + getCoefficients(setA, cbind(setD, setE, setF))[2]*setD + getCoefficients(setA, cbind(setD, setE, setF))[3]*setE + getCoefficients(setA, cbind(setD, setE, setF))[4]*setF)

model4 = (getCoefficients(setA, cbind(setB, setD, setE, setF))[1] + getCoefficients(setA, cbind(setB, setD, setE, setF))[2]*setB + getCoefficients(setA, cbind(setB, setD, setE, setF))[3]*setD + getCoefficients(setA, cbind(setB, setD, setE, setF))[4]*setE) + getCoefficients(setA, cbind(setB, setD, setE, setF))[5]*setF

model5 = (getCoefficients(setA, df)[1] + getCoefficients(setA, df)[2]*setB + getCoefficients(setA, df)[3]*setC + getCoefficients(setA, df)[4]*setD + getCoefficients(setA, df)[5]*setE + getCoefficients(setA, df)[6]*setF)

colnames(model1) = c("Model 1")
colnames(model2) = c("Model 2")
colnames(model3) = c("Model 3")
colnames(model4) = c("Model 4")
colnames(model5) = c("Model 5")

adjrsq = rep(0, 5)
adjrsq[1] = getAdjRsq(setA, model1, 1)
adjrsq[2] = getAdjRsq(setA, model2, 2)
adjrsq[3] = getAdjRsq(setA, model3, 3)
adjrsq[4] = getAdjRsq(setA, model4, 4)
adjrsq[5] = getAdjRsq(setA, model5, 5)
bestModel = which.max(adjrsq)
#Based on this, the best model is model1
adjrsq[bestModel]
setAtest = CFLT[47:length(CFLT)]
setFtest = PTON[47:length(CFLT)]
model1test = getCoefficients(setAtest, setFtest)[1] + getCoefficients(setAtest, setFtest)[2]*setFtest
yTest = CFLT[47:length(CFLT)]
getMSE(yTest, model1test)
```

Step 4:
```{r, warning=FALSE}
setA = CFLT[1:46]
setB = AMD[1:46]
setBsq = setB^2
setC = CS[1:46]
setCsq = setC^2
setD = ATAT[1:46]
setDsq = setD^2
setE = YMM[1:46]
setEsq = setE^2
setF = PTON[1:46]
setFsq = setF^2
df = cbind(setB, setBsq, setC, setCsq, setD, setDsq, setE, setEsq, setF, setFsq)
df1 = cbind(setF)
df2 = cbind(setF, setFsq)
df3 = cbind(setF, setFsq, setB)
df4 = cbind(setF, setFsq, setB, setDsq)
df5 = cbind(setF, setFsq, setB, setDsq, setE)
df6 = cbind(setF, setFsq, setB, setDsq, setE, setEsq)
df7 = cbind(setF, setFsq, setB, setDsq, setE, setEsq, setD)
df8 = cbind(setF, setFsq, setB, setDsq, setE, setEsq, setD, setBsq)
df9 = cbind(setF, setFsq, setB, setDsq, setE, setEsq, setD, setBsq, setCsq)
df10 = cbind(setF, setFsq, setB, setDsq, setE, setEsq, setD, setBsq, setCsq, setC)


model1 = getCoefficients(setA, df1)[1] + getCoefficients(setA, df1)[2]*setF

model2 = getCoefficients(setA, df2)[1] + getCoefficients(setA, df2)[2]*setF + getCoefficients(setA, df2)[3]*setFsq

model3 = getCoefficients(setA, df3)[1] + getCoefficients(setA, df3)[2]*setF + getCoefficients(setA, df3)[3]*setFsq + getCoefficients(setA, df3)[4]*setB

model4 = getCoefficients(setA, df4)[1] + getCoefficients(setA, df4)[2]*setF + getCoefficients(setA, df4)[3]*setFsq + getCoefficients(setA, df4)[4]*setB + getCoefficients(setA, df4)[5]*setDsq

model5 = getCoefficients(setA, df5)[1] + getCoefficients(setA, df5)[2]*setF + getCoefficients(setA, df5)[3]*setFsq + getCoefficients(setA, df5)[4]*setB + getCoefficients(setA, df5)[5]*setDsq + getCoefficients(setA, df5)[6]*setE

model6 = getCoefficients(setA, df6)[1] + getCoefficients(setA, df6)[2]*setF + getCoefficients(setA, df6)[3]*setFsq + getCoefficients(setA, df6)[4]*setB + getCoefficients(setA, df6)[5]*setDsq + getCoefficients(setA, df6)[6]*setE + getCoefficients(setA, df6)[7]*setEsq

model7 = getCoefficients(setA, df7)[1] + getCoefficients(setA, df7)[2]*setF + getCoefficients(setA, df7)[3]*setFsq + getCoefficients(setA, df7)[4]*setB + getCoefficients(setA, df7)[5]*setDsq + getCoefficients(setA, df7)[6]*setE + getCoefficients(setA, df7)[7]*setEsq + getCoefficients(setA, df7)[8]*setD

model8 = getCoefficients(setA, df8)[1] + getCoefficients(setA, df8)[2]*setF + getCoefficients(setA, df8)[3]*setFsq + getCoefficients(setA, df8)[4]*setB + getCoefficients(setA, df8)[5]*setDsq + getCoefficients(setA, df8)[6]*setE + getCoefficients(setA, df8)[7]*setEsq + getCoefficients(setA, df8)[8]*setD + getCoefficients(setA, df8)[9]*setBsq

model9 = getCoefficients(setA, df9)[1] + getCoefficients(setA, df9)[2]*setF + getCoefficients(setA, df9)[3]*setFsq + getCoefficients(setA, df9)[4]*setB + getCoefficients(setA, df9)[5]*setDsq + getCoefficients(setA, df9)[6]*setE + getCoefficients(setA, df9)[7]*setEsq + getCoefficients(setA, df9)[8]*setD + getCoefficients(setA, df9)[9]*setBsq + getCoefficients(setA, df9)[10]*setCsq

model10 = getCoefficients(setA, df10)[1] + getCoefficients(setA, df10)[2]*setF + getCoefficients(setA, df10)[3]*setFsq + getCoefficients(setA, df10)[4]*setB + getCoefficients(setA, df10)[5]*setDsq + getCoefficients(setA, df10)[6]*setE + getCoefficients(setA, df10)[7]*setEsq + getCoefficients(setA, df10)[8]*setD + getCoefficients(setA, df10)[9]*setBsq + getCoefficients(setA, df10)[10]*setCsq + getCoefficients(setA, df10)[11]*setC


colnames(model1) = c("Model 1")
colnames(model2) = c("Model 2")
colnames(model3) = c("Model 3")
colnames(model4) = c("Model 4")
colnames(model5) = c("Model 5")
colnames(model6) = c("Model 6")
colnames(model7) = c("Model 7")
colnames(model8) = c("Model 8")
colnames(model9) = c("Model 9")
colnames(model10) = c("Model 10")

adjrsq = rep(0, 10)
adjrsq[1] = getAdjRsq(setA, model1, 1)
adjrsq[2] = getAdjRsq(setA, model2, 2)
adjrsq[3] = getAdjRsq(setA, model3, 3)
adjrsq[4] = getAdjRsq(setA, model4, 4)
adjrsq[5] = getAdjRsq(setA, model5, 5)
adjrsq[6] = getAdjRsq(setA, model1, 6)
adjrsq[7] = getAdjRsq(setA, model2, 7)
adjrsq[8] = getAdjRsq(setA, model3, 8)
adjrsq[9] = getAdjRsq(setA, model4, 9)
adjrsq[10] = getAdjRsq(setA, model5, 10)
bestModel = which.max(adjrsq)
#Based on this, the best model is model6
adjrsq[bestModel]
setAtest = CFLT[47:length(CFLT)]
setBtest = AMD[47:length(AMD)]
setBsqtest = setBtest^2
setCtest = CS[47:length(CS)]
setCsqtest = setCtest^2
setDtest = ATAT[47:length(ATAT)]
setDsqtest = setDtest^2
setEtest = YMM[47:length(YMM)]
setEsqtest = setEtest^2
setFtest = PTON[47:length(PTON)]
setFsqtest = setFtest^2
df6test = cbind(setFtest, setFsqtest, setBtest, setDsqtest, setEtest, setEsqtest)
prediction = getCoefficients(setAtest, df6test)[1] + getCoefficients(setAtest, df6test)[2]*setFtest + getCoefficients(setAtest, df6test)[3]*setFsqtest + getCoefficients(setAtest, df6test)[4]*setBtest + getCoefficients(setAtest, df6test)[5]*setDsqtest + getCoefficients(setAtest, df6test)[6]*setEtest + getCoefficients(setAtest, df6test)[7]*setEsqtest
yTest = CFLT[47:length(CFLT)]
getMSE(yTest, prediction)
```

```{r}
getSymbols("DAL", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
getSymbols("NET", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
getSymbols("MTCH", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
getSymbols("JPM", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
getSymbols("MDB", from = "2023-01-26", to = "2023-04-26", warnings = FALSE, auto.assign = TRUE)
DAL = c(DAL$DAL.Adjusted)
NET = c(NET$NET.Adjusted)
MTCH =c(MTCH$MTCH.Adjusted)
JPM = c(JPM$JPM.Adjusted)
MDB = c(MDB$MDB.Adjusted)
```

step5:
```{r, warning=FALSE, error=FALSE}
setA = CFLT[1:46]
setB = AMD[1:46]
setBsq = setB^2
setC = CS[1:46]
setCsq = setC^2
setD = ATAT[1:46]
setDsq = setD^2
setE = YMM[1:46]
setEsq = setE^2
setF = PTON[1:46]
setFsq = setF^2
setG = DAL[1:46]
setH = NET[1:46]
setI = MTCH[1:46]
setJ = JPM[1:46]
setK = MDB[1:46]

df = cbind(setB, setBsq, setC, setCsq, setD, setDsq, setE, setEsq, setF, setFsq, setG, setH, setI, setJ, setK)

forward_subset_selection(setA, df)

df1 = cbind(setK)
df2 = cbind(setK, setF)
df3 = cbind(setK, setF, setH)
df4 = cbind(setK, setF, setH, setD)
df5 = cbind(setK, setF, setH, setD, setJ)
df6 = cbind(setK, setF, setH, setD, setJ, setC)
df7 = cbind(setK, setF, setH, setD, setJ, setC, setI)
df8 = cbind(setK, setF, setH, setD, setJ, setC, setI, setG)
df9 = cbind(setK, setF, setH, setD, setJ, setC, setI, setG, setE)
df10 = cbind(setK, setF, setH, setD, setJ, setC, setI, setG, setE, setBsq)
df11 = cbind(setK, setF, setH, setD, setJ, setC, setI, setG, setE, setBsq, setB)
df12 = cbind(setK, setF, setH, setD, setJ, setC, setI, setG, setE, setBsq, setB, setCsq)
df13 = cbind(setK, setF, setH, setD, setJ, setC, setI, setG, setE, setBsq, setB, setCsq, setDsq)
df14 = cbind(setK, setF, setH, setD, setJ, setC, setI, setG, setE, setBsq, setB, setCsq, setDsq, setFsq)
df15 = cbind(setK, setF, setH, setD, setJ, setC, setI, setG, setE, setBsq, setB, setCsq, setDsq, setFsq, setEsq)

coefficients1 = getCoefficients(setA, df1)
model1 = coefficients1[1] + coefficients1[2]*setK

coefficients2 = getCoefficients(setA, df2)
model2 = coefficients2[1] + coefficients2[2]*setK + coefficients2[3]*setF

coefficients3 = getCoefficients(setA, df3)
model3 = coefficients3[1] + coefficients3[2]*setK + coefficients3[3]*setF + coefficients3[4]*setH

coefficients4 = getCoefficients(setA, df4)
model4 = coefficients4[1] + coefficients4[2]*setK + coefficients4[3]*setF + coefficients4[4]*setH + coefficients4[5]*setD

coefficients5 = getCoefficients(setA, df5)
model5 = coefficients5[1] + coefficients5[2]*setK + coefficients5[3]*setF + coefficients5[4]*setH + coefficients5[5]*setD + coefficients5[6]*setJ

coefficients6 = getCoefficients(setA, df6)
model6 = coefficients6[1] + coefficients6[2]*setK + coefficients6[3]*setF + coefficients6[4]*setH + coefficients6[5]*setD + coefficients6[6]*setJ + coefficients6[7]*setC

coefficients7 = getCoefficients(setA, df7)
model7 = coefficients7[1] + coefficients7[2]*setK + coefficients7[3]*setF + coefficients7[4]*setH + coefficients7[5]*setD + coefficients7[6]*setJ + coefficients7[7]*setC + coefficients7[8]*setI

coefficients8 = getCoefficients(setA, df8)
model8 = coefficients8[1] + coefficients8[2]*setK + coefficients8[3]*setF + coefficients8[4]*setH + coefficients8[5]*setD + coefficients8[6]*setJ + coefficients8[7]*setC + coefficients8[8]*setI + coefficients8[9]*setG

coefficients9 = getCoefficients(setA, df9)
model9 = coefficients9[1] + coefficients9[2]*setK + coefficients9[3]*setF + coefficients9[4]*setH + coefficients9[5]*setD + coefficients9[6]*setJ + coefficients9[7]*setC + coefficients9[8]*setI + coefficients9[9]*setG + coefficients9[10]*setE

coefficients10 = getCoefficients(setA, df10)
model10 = coefficients10[1] + coefficients10[2]*setK + coefficients10[3]*setF + coefficients10[4]*setH + coefficients10[5]*setD + coefficients10[6]*setJ + coefficients10[7]*setC + coefficients10[8]*setI + coefficients10[9]*setG + coefficients10[10]*setE + coefficients10[11]*setBsq

coefficients11 = getCoefficients(setA, df11)
model11 = coefficients11[1] + coefficients11[2]*setK + coefficients11[3]*setF + coefficients11[4]*setH + coefficients11[5]*setD + coefficients11[6]*setJ + coefficients11[7]*setC + coefficients11[8]*setI + coefficients11[9]*setG + coefficients11[10]*setE + coefficients11[11]*setBsq + coefficients11[12]*setB

coefficients12 = getCoefficients(setA, df12)
model12 = coefficients12[1] + coefficients12[2]*setK + coefficients12[3]*setF + coefficients12[4]*setH + coefficients12[5]*setD + coefficients12[6]*setJ + coefficients12[7]*setC + coefficients12[8]*setI + coefficients12[9]*setG + coefficients12[10]*setE + coefficients12[11]*setBsq + coefficients12[12]*setB + coefficients12[13]*setCsq

coefficients13 = getCoefficients(setA, df13)
model13 = coefficients13[1] + coefficients13[2]*setK + coefficients13[3]*setF + coefficients13[4]*setH + coefficients13[5]*setD + coefficients13[6]*setJ + coefficients13[7]*setC + coefficients13[8]*setI + coefficients13[9]*setG + coefficients13[10]*setE + coefficients13[11]*setBsq + coefficients13[12]*setB + coefficients13[13]*setCsq + coefficients13[14]*setDsq

coefficients14 = getCoefficients(setA, df14)
model14 = coefficients14[1] + coefficients14[2]*setK + coefficients14[3]*setF + coefficients14[4]*setH + coefficients14[5]*setD + coefficients14[6]*setJ + coefficients14[7]*setC + coefficients14[8]*setI + coefficients14[9]*setG + coefficients14[10]*setE + coefficients14[11]*setBsq + coefficients14[12]*setB + coefficients14[13]*setCsq + coefficients14[14]*setDsq + coefficients14[15]*setFsq

coefficients15 = getCoefficients(setA, df15)
model15 = coefficients15[1] + coefficients15[2]*setK + coefficients15[3]*setF + coefficients15[4]*setH + coefficients15[5]*setD + coefficients15[6]*setJ + coefficients15[7]*setC + coefficients15[8]*setI + coefficients15[9]*setG + coefficients15[10]*setE + coefficients15[11]*setBsq + coefficients15[12]*setB + coefficients15[13]*setCsq + coefficients15[14]*setDsq + coefficients15[15]*setFsq + coefficients15[16]*setEsq

colnames(model1) = c("Model 1")
colnames(model2) = c("Model 2")
colnames(model3) = c("Model 3")
colnames(model4) = c("Model 4")
colnames(model5) = c("Model 5")
colnames(model6) = c("Model 6")
colnames(model7) = c("Model 7")
colnames(model8) = c("Model 8")
colnames(model9) = c("Model 9")
colnames(model10) = c("Model 10")
colnames(model11) = c("Model 11")
colnames(model12) = c("Model 12")
colnames(model13) = c("Model 13")
colnames(model14) = c("Model 14")
colnames(model15) = c("Model 15")

adjrsq = rep(0, 15)
adjrsq[1] = getAdjRsq(setA, model1, 1)
adjrsq[2] = getAdjRsq(setA, model2, 2)
adjrsq[3] = getAdjRsq(setA, model3, 3)
adjrsq[4] = getAdjRsq(setA, model4, 4)
adjrsq[5] = getAdjRsq(setA, model5, 5)
adjrsq[6] = getAdjRsq(setA, model6, 6)
adjrsq[7] = getAdjRsq(setA, model7, 7)
adjrsq[8] = getAdjRsq(setA, model8, 8)
adjrsq[9] = getAdjRsq(setA, model9, 9)
adjrsq[10] = getAdjRsq(setA, model10, 10)
adjrsq[11] = getAdjRsq(setA, model11, 11)
adjrsq[12] = getAdjRsq(setA, model12, 12)
adjrsq[13] = getAdjRsq(setA, model13, 13)
adjrsq[14] = getAdjRsq(setA, model14, 14)
adjrsq[15] = getAdjRsq(setA, model15, 15)
bestModel = which.max(adjrsq)
#Based on this, the best model is model1
adjrsq[bestModel]
setKtest = MDB[47:length(MDB)]
coefficientstest = getCoefficients(setAtest, setKtest)
prediction = coefficientstest[1] + coefficientstest[2]*setKtest
yTest = CFLT[47:length(CFLT)]
getMSE(yTest, prediction)
```

step6:

The model with the lowest MSE was step 4. This is good because it indicates that the model is accurately predicting the target variable, meaning that it is making fewer errors. A low MSE can also be a sign that the model is not overfitting the data, meaning it starts to memorize the training data instead of learning the underlying patterns which can lead to poor performance on new data. When comparing multiple models, the one with the lowest MSE is generally considered to be the best performing.
The model with the highest adjusted R^2 is step 5. This is good because it indicates that the independent variables in the model are good predictors of the dependent variable. It can also help to identify which independent variables are most important in predicting the dependent variable, by looking at the coefficients of the independent variables in the model. When comparing multiple models, the one with the highest adjusted R-squared is generally considered to be the best performing.
The optimal model we would rely on would be step 4 because it has the lowest MSE, however the model with the largest adjusted R squared is the model from step 5, meaning it was a better fit for the training data, however it wasn't as good of a predictor as the model from step 4.